### 2022-03-22 TP3/cod/tex/preamble.tex
transfer

@@

\newcommand{\asgold}[1]{\textcolor{mygold}{{\bf#1}}}
\newcommand{\asgrey}[1]{\textcolor{gray}{{\bf#1}}}
\newcommand{\asred}[1]{\textcolor{red}{{\bf#1}}}
\newcommand{\asor}[1]{\textcolor{orange}{{\bf#1}}}
\newcommand{\ascy}[1]{\textcolor{cyan}{{\bf#1}}}
\newcommand{\asgr}[1]{\textcolor{mygreen}{{\bf#1}}}
\newcommand{\aspurp}[1]{\textcolor{mypurp}{{\bf#1}}}

>>>>

\definecolor{commentGray}{RGB}{128, 128, 128}
\definecolor{parentBlue}{RGB}{61, 61, 255}

\definecolor{objectPurp}{RGB}{218, 110, 191}
\definecolor{backgroundDarkPurp}{RGB}{38, 35, 53}
\definecolor{basicText}{RGB}{147, 147, 151}
\definecolor{functionColor}{RGB}{51, 232, 231}
\definecolor{typeRed}{RGB}{254, 68, 80}

@@

\newcommand{\asgold}[1]{\textcolor{mygold}{{\bf#1}}}
\newcommand{\asgrey}[1]{\textcolor{gray}{{\bf#1}}}
\newcommand{\asred}[1]{\textcolor{red}{{\bf#1}}}
\newcommand{\asor}[1]{\textcolor{orange}{{\bf#1}}}
\newcommand{\ascy}[1]{\textcolor{cyan}{{\bf#1}}}
\newcommand{\asgr}[1]{\textcolor{mygreen}{{\bf#1}}}
\newcommand{\aspurp}[1]{\textcolor{mypurp}{{\bf#1}}}
\newcommand{\astype}[1]{\textcolor{typeRed}{\texttt{#1}}}

%%% LSTLISTINGS CONFIG:
\lstset{ %
  backgroundcolor=\color{backgroundDarkPurp},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
  basicstyle=\footnotesize\color{basicText},        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{commentGray}\textit,    % comment style
  deletekeywords={set, min, max, seq},            % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  escapechar={|},
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  frame=tb,	                   	   % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
%   keywordstyle=\color{objectPurp}\bfseries,       % keyword style
%   keywordstyle[2]\color{functionColor},
  language=C,                 % the language of the code (can be overrided per snippet)
%   otherkeywords={root,...},           % if you want to add more keywords to the set
  numbers=none,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{green}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{purple}, % string literal style
  tabsize=2,	                   % sets default tabsize to 2 spaces
  classoffset=0,
  morekeywords={addKeyBST},
  morekeywords=[2]{root},
  keywordstyle=[2]\color{objectPurp},
  title=\lstname,                  % show the filename of files included with \lstinputlisting; also try caption instead of title
  columns=fixed,                    % Using fixed column width (for e.g. nice alignment)
%   literate={\{}{{\CodeSymbol{\{}}}1
%            {\}}{{\CodeSymbol{\}}}}1
%         %    {(}{{\CodeSymbol{(}}}1
        %    {~)}{{\CodeSymbol{)}}}1
        %    {>}{{\CodeSymbol{$>$}}}1
        %    {=}{{\CodeSymbol{$=$}}}1
        %    {;}{{\CodeSymbol{$;$}}}1
}
